\documentclass[11pt,final,a4paper]{que_cv}
\def\ASDIR{../assets}
\begin{document}
\pagenumbering{gobble}
%
\setlogo{\ASDIR/abyss}
\setname{John Doe}
\setphone{000-000-0000}
\setemail{john.doe@outlook.com}
\setwebsite{johndoe.com}
\setaddress{123 Main Street, San Francisco, CA 94122}
%
\showinfo
%
\begin{cvsection}{Education}
  \cvsubsection{California Technical University}{}{Aug 1998 $\sim$ Dec 2002}
  \desclabel{Degree} Ph.D in Astronomy\\
  \desclabel{Courses} Introduction to Astronomy, Frontiers and Controversies in Astrophysics
\end{cvsection}
%
\begin{cvsection}{Experiences}
  \cvsubsection{Cleveland OH Astronomer}{National Aeronautics}{Jan 2007 $\sim$ Aug 2014}
  \begin{entrylist}
  \item Analyzed large data sets collected through observatories and satellites. \item Prepared reports on research findings.
  \item Gathered data to aid in navigation, satellite technology and space exploration.
  \item Through applied research, developed computer software to assist in accurate observations and data collection.
  \end{entrylist}
  \cvsubsection{New York NY Astronomer}{Columbia University}{May 2002 $\sim$ Jul 2007}
  \begin{entrylist}
  \item Worked on research project funded by grants.
  \item Wrote grant proposals.
  \item Traveled to remote locations and often worked at night for better observation conditions.
  \item Assisted in the development of computer software to analyze data.
  \item Analyzed astronomical and physical data through complex mathematical calculations.
  \end{entrylist}
  \cvsubsection{Post-doctoral Research}{The Goddard Institute}{Aug 1998 $\sim$ Mar 2002}
  \begin{entrylist}
  \item Worked with ground-based telescopes to observe the movements of stars, planets and galaxies.
  \item Authored scientific papers for journals.
  \item Designed telescopes, lasers and other scientific equipment.
  \item Conducted applied research related to GPS technology.
  \end{entrylist}
\end{cvsection}
%
\begin{cvsection}{Qualifications}
  \cvsubsection{Skills}{}{}
  \begin{entrylist}
  \item Complex problem solving
  \item Advanced mathematical and science skills
  \item Teamwork
  \item Development of techniques to collect and study astronomical data
  \item Strong physics background
  \end{entrylist}
  \cvsubsection{Programming}{}{}
  \begin{hentrylist}
  \item R
  \item Java
  \item Python
  \item JavaScript
  \item Web Development
  \end{hentrylist}
  \cvsubsection{Design}{}{}
  \begin{hentrylist}
  \item Photoshop
  \item Illustrator
  \item Prototyping
  \item UI design
  \item Latex
  \end{hentrylist}

\end{cvsection}
%
\begin{cvsection}{Activities}
  \cvsubsection{Member}{Tau Beta Pi Engineering Honor Society}{}
  Ate a lot of pies.
  \cvsubsection{Member}{National Society of Collegiate Scholars}{}
  Drank a lof of wine.
  \cvsubsection{Hobbies}{}{}
  Photography, handicrafts, traveling and arts.
\end{cvsection}
%
\end{document}
